Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-08-15 patchy-selection-paper.tex
minor changes

If the influx is higher -- say, $\rho A \mu = .01$,
the required separation between patches is only reduced to $R/\sigma > 7.3$ with $s_m=.05$.
If $\rho A \mu = .01$ and $s_m=.001$, then the prediction is that mutation will \emph{always} be faster than migration
-- however, with $s_m=.001$, for the assumption of well-separated patches to hold we would need $R/\sigma > 1/\sqrt{2s_m} = 22.4$;
therefore, at spatial scales smaller than about 20 dispersal distances the model breaks down.

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics{phase-diagram-log}
  \end{center}
  \caption{
  Shaded contour plots of
  mean time until adaptation in a new patch occurs by migration ($\Tmig$, blue) or by mutation ($\Tmut$, red),
  as a function of population density ($\rho$), 
  distance to an already adapted patch in units of dispersal distance ($R/\sigma$),
  strength of deleterious selection ($s_m$),
  and mutation rate scaled by patch area ($\mu A$).
  The right-hand plot shows that $\migrate$ is relatively insensitive to $s_m$.
  The black, dotted line shows values where $\Tmig=\Tmut$.
  Default parameter values were $A=100$, $\rho=10$, $\mu=10^{-8}$, $s_p=0.1$, $s_m=0.01$, $R/\sigma=20$, and $\xi^2=1$.
  Note that population density $\rho$ and mutation influx $A\mu$ are shown on a log scale.
  \label{fig:phase_diagram}
  }
\end{figure}

>>>>

If the mutational influx is higher -- say, $\rho A \mu = .01$ --
the required separation between patches is only reduced to $R/\sigma > 7.3$ with $s_m=.05$.
If $s_m=.001$, then with this higher mutational influx this calculation predicts that mutation will \emph{always} be faster than migration
-- however, this is misleading, 
since with $s_m=.001$, for the assumption of well-separated patches to hold we would need $R/\sigma > 1/\sqrt{2s_m} = 22.4$.
The correct conclusion is that convergent adaptation is much more likely than shared adaptation
between patches separated by at least 22.4$\sigma$;
for shorter separations the model breaks down.

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics{phase-diagram-log}
  \end{center}
  \caption{
  Shaded contour plots of
  mean time until adaptation in a new patch occurs by migration ($\Tmig$, blue) or by mutation ($\Tmut$, red),
  as a function of population density ($\rho$), 
  distance to an already adapted patch in units of dispersal distance ($R/\sigma$),
  strength of deleterious selection ($s_m$),
  and mutation rate scaled by patch area ($\mu A$).
  The right-hand plot shows that $\migrate$ is relatively insensitive to $s_m$ (thanks to the square root).
  The black, dotted line shows values where $\Tmig=\Tmut$.
  Default parameter values were $A=100$, $\rho=10$, $\mu=10^{-8}$, $s_p=0.1$, $s_m=0.01$, $R/\sigma=20$, and $\xi^2=1$.
  Note that population density $\rho$ and mutation influx $A\mu$ are shown on a log scale.
  \label{fig:phase_diagram}
  }
\end{figure}
